### 2025-08-17 correlation.qmd
20250817 - correlation ratio

mod <- stats::aov(
  fantasyPoints ~ height,
  data = player_stats_seasonal)

correlationRatio <- effectsize::eta_squared(mod)

@@

correlationRatio[cols_to_sqrt] <- sqrt(correlationRatio[cols_to_sqrt])

@@

correlationRatio
```

>>>>

mod <- stats::aov(
  fantasyPoints ~ factor(height), # convert the predictor variable to a categorical variable (i.e., factor); if there are too many unique values, can also consider binning the variable into ranges
  data = player_stats_seasonal)

etaSquared <- effectsize::eta_squared(mod)
print(etaSquared, digits = 9)

correlationRatio <- etaSquared

@@

correlationRatio[cols_to_sqrt] <- sqrt(correlationRatio[cols_to_sqrt]) # take the square root of eta-squared to get eta

@@

print(correlationRatio, digits = 9)

# the correlation ratio (eta) is equivalent to square root of R-squared (when the predictor is converted to a factor)
Rsquared <- summary(stats::lm(
  fantasyPoints ~ factor(height),
  data = player_stats_seasonal))$r.squared

Rsquared

Rvalue <- sqrt(Rsquared)
Rvalue
```
